---
title: "Statistical_Inference_-_ToohGrowth Analysis"
author: "Joel Calixto"
date: "5 de junio de 2016"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Statistical Inference - Toohgrowth analysis

In this project correspond analysis of tooth growth influencied by supplement type and dose

# Point 1 
Load the ToothGrowth data and perform some basic exploratory data analyses

```{r load}
#load plot package
library(ggplot2)
#take a datasets of example 
data("ToothGrowth")

#check type of type and variables
str(ToothGrowth)

#show a previous of data
head(ToothGrowth)

#show a plot of data for explore data
ggplot(data=ToothGrowth, aes(x=dose, y=len, fill=supp)) + geom_bar(stat="identity",) + facet_grid(. ~ supp) + xlab("Dose in mgs") + ylab("Tooth") + guides(fill=guide_legend(title="Supplement type"))

#check len of tooth by dose
ggplot(aes(x=supp, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp)) + xlab("Supplement") + ylab("Tooth Length") + facet_grid(~ dose) + ggtitle("Tooth Length /Dose") + 
     theme(plot.title = element_text(lineheight=.2))

#check len of tooth by supplement type
ggplot(aes(x=supp, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp)) + xlab("Type of Supplement") + ylab("Tooth height") + guides(fill=guide_legend(title="Supplement type"))

```

# Point 2
Provide a basic summary of the data.

```{r summary}
#display a summary of data 
summary(ToothGrowth)
```

# Point 3
Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

We can see that p-value is more great than 0.05 =0.06063 and confidence intervals contains zero, then can not reject NULL hypothesis
```{r analysis}

#compare tooth growth grouping by supplement
t.test(len~supp,data=ToothGrowth)
```

In next combination of dose we can see that p-value is 1.268e-07,  4.398e-14, 1.906e-05 respectively
and confidence invervals do not contains 0 from this way we can reject NULL hypothesis

```{r analysis combination}
# generate a var of group combination
doses_com1 <- subset (ToothGrowth, dose %in% c(0.5, 1.0)) 
doses_com2 <- subset (ToothGrowth, dose %in% c(0.5, 2.0)) 
doses_com3 <- subset (ToothGrowth, dose %in% c(1.0, 2.0)) 

# Check for combination 0.5 and 1.0 mg
t.test(len ~ dose, data = doses_com1)
# Check for combination 0.5 and 2.0 mg
t.test(len ~ dose, data = doses_com2)
# Check for combination 1.0 and 2.0 mg
t.test(len ~ dose, data = doses_com3)
```

#Point 4
State your conclusions and the assumptions needed for your conclusions. 

With the results above we can conclude
1.- Type of supplement does NOT affect in grow of tooth
2.- Dose of supplement YES can influence grow the tooth

